---
title: "Using the Binomial Package"
author: "Terence Wilson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the Binomial Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(Binomial)
```

## Introduction

`"Binomial"` is a package which give you the capability to calbulate various 
binomial probabilities using a range of different features. 


## Binomial functions

To get a simple choose result for a binomial function, just use the bin_choose 
function

```{r}
bin_choose(5, 2)

bin_choose(5, 1:2)
```

If you woud like the probability of getting a particular number of successes, use
the bin_probability function, with the added probability input.

```{r}
bin_probability(3, 5, 0.5)

```

You can use the functions bin_variable, bin_distribution, and bin_cumulative to create
binvar, bindis, and bincum objects, which each hve their own uses.



## Bin_variable


bin_variable takes trials and probability, and creates a binvar object, which has the methods
print and summary. These methods can be used like so:

```{r}
bivar <- bin_variable(5, 0.5)
```


## Bin_distribution

This function creates a bindis object, which has the method plot.

bin_distribution can be used like so:

```{r}

bidis <- bin_distribution(5, 0.2)
plot(bidis)

``` 

This will return a bar chart of the probability of achieving each success
from 0 to number of trials.

##Bin_cumulative

This function creates a bincum object, which has the method plot.

bin_cumulative can be used like so:

 
```{r}

bidis <- bin_distribution(5, 0.2)
plot(bidis)
```
This will return a line-point plot of the probability of achieving each success
from 0 to number of trials, cumulative on the previous trial probabilities.

#Single vairable functions

If you would like to know just a single feature of a binomial distribution, there
are five functions which do so.
bin_mean(trials, prob) -- returns the mean of a binomial distribution
bin_mode(trials, prob) -- returns the mode of a binomial distribution
bin_variance(trials, prob) -- returns the variance of a binomial distribution
bin_skewness(trials, prob) -- returns the skewness of a binomial distribution
bin_kurtosis(trials, prob) -- returns the curve value of a binomial distribution.
---







